Title

### 2021-09-10 paper/main.tex
Syncing before going to the lab

Where the near and free states are defined based on the
distance between the graphene layer and the $\alpha-$carbon of the
amino acid projected onto a vector normal to the graphene layer. For a
graphene layer prepared along the XY plane, this is equivalent to the
distance along the Z--axis. This distance will be defined as the
reaction coordinate $\xi$. The cut-off ranges for the near and far
states will be defined based on the PMFs (potentials of mean force)
along $\xi$ of the amino acids, which can be found in the
supplementary materials \textcolor{red}{TODO}.

@@

\begin{equation}
\label{eq:Aads-from-PMF-p}
\Delta A^{ads} = - k_B T \ln \left(\frac{\sum_{j \in near} p_{\xi_j}}{\sum_{k \in free} p_{\xi_k}}\right)
\end{equation}
On the following sections, two different methods used to obtain a PMF along $\xi$ will be described.

@@

>>>>

Where the near and free states are defined based on the reaction
coordinate $\xi(\mathbf{r})$. $\xi(\mathbf{r})$ depends on the
coordinates of the system ($\mathbf{r}$) and is equal to the distance
between the graphene layer and the $\alpha-$carbon of the amino acid
projected onto a vector normal to the graphene layer. For a graphene
layer prepared along the XY plane, this is equivalent to the distance
along the Z--axis. The cut-off ranges for the near and far states will
be defined based on the PMFs (potentials of mean force) along $\xi(\mathbf{r})$ of
the amino acids, which can be found in the supplementary materials
\textcolor{red}{TODO}.

@@

\begin{equation}
\label{eq:Aads-from-PMF-p}
\Delta A^{ads} = - k_B T \ln \left(\frac{\sum_{j \in near} p_{\xi_j}}{\sum_{k \in free} p_{\xi_k}}\right)
\end{equation}

On the following sections, two different methods used to obtain a PMF along $\xi$ will be described.

@@

Umbrella sampling\cite{Torrie_1977} was used to obtain the PMF along
reaction coordinate by sampling multiple windows of $\xi$. Each sample
was obtained from a simulation where the Hamiltonian included the
following potential:

\begin{equation}
\label{eq:umbrella-potential}
\mathcal{V}^{US}(\mathbf{r}, k^{US}, \xi^0) = \frac{1}{2}k^{US}[\xi^0
- \xi(\mathbf{r})]^2
\end{equation}

where $\xi^0$ is the center of the sampling window and $k^{US}$ is an
harmonic constant. For simulations of amino acids over pristine
graphene $\xi^0$ took values from 0.3 to 1.5 nm in 0.05 nm steps, while $k^{US}$ took
values from 1000 to 12000 [$kJ \cdot mol \cdot nm^2$] adjusted to
ensure a good overlap in the sampling of different windows while
retaining a high sampling of the window's center.

The biased samples of $\xi$ obtained from these windows were used
to obtain the unbiased PMF using an implementation of the Weighted Histogram Analysis
Method (WHAM)\cite{Kumar_1992, Kumar_1995} developed by
\citet{WHAM}. This implementation of WHAM outputs --in addition to the
free energy/probability along $\xi$-- the (dimensionless) free energy
of each window, $F_i$. Knowing the $F_i$ of every we can unbias our
samples of any property $T$, to get an average for the window:

\begin{equation}
\label{eq:WHAM-unbias}
\langle T(\xi') \rangle = \frac{\sum_i^{S} \sum_j^{N_i} T_{i, j}
  e^{-\beta[F_i - \mathcal{V}^{US}(\mathbf{r_j})]}
  \delta \xi_{i, j}}{\sum_i^{S} \sum_j^{N_i}
  e^{-\beta[F_i - \mathcal{V}^{US}(\mathbf{r_j})]}
  \delta \xi_{i, j}}
\end{equation}

where $$
